cardinalR: Generating interesting high-dimensional data structures

### 2025-09-19 paper-cardinalR.tex
more clear about the p

The main function of the package is \texttt{gen\_multicluster()}, which generates datasets consisting of multiple clusters with user-specified characteristics. Users can control the number of clusters (\texttt{k}), the number of points in each cluster (\texttt{n}), and the dimensionality of the space (\texttt{p}). Each cluster can take on a different geometric shape (e.g., Gaussian, cone, uniform cube), be scaled to adjust its spread, rotated in specified planes by given angles, and positioned at defined centroids (\texttt{loc}). The function ensures flexibility in cluster location and orientation, allowing users to simulate complex high-dimensional structures. An optional argument, \texttt{is\_bkg}, adds background noise drawn from a multivariate normal distribution centered on the dataset's overall mean with standard deviations matching the observed spread.

>>>>

The main function of the package is \texttt{gen\_multicluster()}, which generates datasets consisting of multiple clusters with user-specified characteristics. Users can control the number of clusters (\texttt{k}), the number of points in each cluster (\texttt{n}), and the dimensionality of the space (\texttt{p}) for all the clusters. Each cluster can take on a different geometric shape (e.g., Gaussian, cone, uniform cube), be scaled to adjust its spread, rotated in specified planes by given angles, and positioned at defined centroids (\texttt{loc}). The function ensures flexibility in cluster location and orientation, allowing users to simulate complex high-dimensional structures. An optional argument, \texttt{is\_bkg}, adds background noise drawn from a multivariate normal distribution centered on the dataset's overall mean with standard deviations matching the observed spread.
